CES Package Writeup

### 2020-08-14 paper.Rmd
Paper update

# Key functions
The main function in `CESR` is.... This takes the following arguments... An example use case for this is...

>>>>

# Key functions
The main function in `CESR` is `get_ces`. This function will return a requested CES survey as a usable data object, a url to the original download destination, and the citation for the survey when provided with an associated survey code.
